---
title: "Processor work report"
author: "Python & R"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    fig_width: 8
    fig_height: 4
    includes:
      in_header: header.tex
---
# Processor work report

## General

This report based on plotting graphs and calculating simple statistics based on log files.

General information based on `General.txt` file:

* `r gen[1]`
* `r gen[2]`

\newpage
## Ethernet stream

Here is a count of full and partial frames in Ethernet stream.

```{r echo = FALSE, fig.height = 8}
plot(ethernet)
```

\newpage
## Analyzing task status

In the plot below presented count of tasks by their status:

* done;
* TTL timeout;
* skipped.

```{r echo = FALSE, fig.height = 8}
plot(dts)
```

\newpage
## Processors distribution

We assume that tasks must distribute uniformly in all processors. Plot below shows real distribution after work of multiprocessing topology.

```{r echo = FALSE, fig.height = 8}
plot(procs)
```

\newpage
## Cores distribution

Below are plots of distribution of tasks by cores inside processor. Here we also assume that this distribution must be uniform.

```{r echo = FALSE, results = "asis", fig.height = 4}
for (i in seq(length(cores))) {
  cat(sprintf("### `%s` Processor\n\n", i-1))
  grid.newpage()
  grid.draw(cores[[i]])
  cat("\n\n")
}
```